---
title: "W201 Portfolio"
author: "Michael Ballschmiede"
date: "MIDS Summer 2017"
site: bookdown::bookdown_site
documentclass: book
---

<!-- This won't be displayed but it will initialize your R session. Add any R libraries you need here. -->
```{r init,include=FALSE,echo=FALSE}
library(magrittr)
```


# Welcome! {-}

Below you'll find two ideas through which I believe an application of data science can markedly improve an existing industry. The first idea, ScalpPlaza, aims to utilize machine learning and advanced market-making trading techniques to revolutionize the secondhand ticket marketplace. The second idea, ReLux, aspires to optimize micro-apartment building layouts in order to provide a modern, luxurious, community-driven, and economically-feasible alternative to city dwellers. While I find both ideas promising I think ScalpPlaza would be easier to implement and has more potential to scale, as I explain in the short video below. 


<!-- Below this line is just examples of how you can embed video from Google Drive. First you have to enable sharing, then just get the object ID which is that long string between d/ and /preview and will also be appended to any sharing link you generate for your video. -->
<p>
```{r hello-benji,echo=FALSE,fig.cap='Hello Benjamin Franklin!',fig.align='center'}
knitr::include_url('https://drive.google.com/file/d/0B6bobRDQR96iVEV3SXJJal9CczQ/preview')
```

### Abstract: ScalpPlaza {-}

While recent history has seen financial marketplaces turned upside-down by artificial intelligence and automation, the secondary ticket marketplace has remained remarkably stagnant. As a result of this lack of innovation, one's options for buying or selling last minute event tickets remain to be exhausting, prone to fraud, and/or costly. ScalpPlaza seeks to provide users with  efficient, two-sided ticket marketplaces for any and all live entertainment events. Unlike most incumbent online ticket exchanges, ScalpPlaza will display both the best bid and and the best offer price for any given ticket. This will allow users to buy or sell tickets in seconds when they’re in a rush or to try “cutting the market” in hopes of getting a better deal when they can afford to be patient. ScalpPlaza’s primary differentiating factor, however, is its ability and willingness to provide market liquidity by transacting with its users and accumulating ticket positions. This will be made possible through the use of a data-driven algorithmic ticket-pricing model. Essentially, ScalpPlaza aims to utilize historical data, market trends, and machine learning predict what a ticket is worth on the open market based on the event’s original ticket price and a multitude of other pertinent intrinsic and extrinsic factors. The model will eventually use this estimated ticket value and a variance metric to generate prices at which ScalpPlaza would be comfortable buying or selling any given ticket. These prices will then drift dynamically based on informational changes, order flow, and ScalpPlaza’s internal ticket inventory. This second revenue stream will allow ScalpPlaza to charge signicantly lower fees than the exorbitant 20% (10% buyer + 10% seller) charged by some of its competitors. Collecting enough data to accurately predict open market ticket values will not happen overnight; however, the relatively low fees ScalpPlaza is willing to offer should serve to draw more and more visitors to the site, speeding up the data collecting process and ultimately resulting in a sustainable and revolutionary secondary ticket marketplace.


### Abstract: ReLux {-}

Urbanization has resulted in a growing disparity between what people who live in cities want in a residence and what they are able to afford. ReLux aspires to provide a modern, luxurious, community-driven, and economically-feasible option to city dwellers by asking them to trade superfluous apartment space for spacious communal areas and top-of-the-line amenities. ReLux hopes to utilize trenchant analysis of intra- and inter-city occupation distributions, cost of living indices, general geographical dispositions, and potential local competition in order to identify and target its most promising launch locations. Equally important will be customizing and tailoring each building's communal areas to local lifestyles and preferences. ReLux hopes to gain a thorough understanding of what people in various locations value in their domestic spaces by supplementing traditional polling data with modern data science. Applying regression analysis, clustering, and other machine learning techniques to the troves of publically available housing data (residential layouts, housing prices, renovation details, etc.) should help ReLux better stay abreast of intra-city, inter-city, and nationwide trends. Admittedly, ReLux is not for everybody; but in an age where [shared workspaces](https://www.cbinsights.com/research/wework-valuation-analysis/) and [tiny homes](http://www.countryliving.com/home-design/g1887/tiny-house/?) are all the rage, ReLux is confident in its ability to carve out a new lifestyle niche and ultimately leverage a "less is more" approach in fostering and maintaining successful communities. 


## About the author {-}

Michael graduated from the University of Wisconsin - Madison in 2012 after receiving his BA in Industrial & Systems Engineering. He soon after moved to Chicago, where he has since remained working for a proprietary trading firm specializing in market-making. While his primary responsibilties include actively trading and managing a U.S. Treasury options portfolio, Michael is also passionate about developing and implementing innovative new trading strategies. Michael joined UC Berkeley's MIDS program in 2017, where he hopes to continue building his analytical toolset in order to tackle ever-bigger and more complex problems. Apart from playing with numbers, Michael enjoys travelling, sports, Larry David brainchildren, Chipotle, flannels, and live music.

*Updated: `r Sys.Date()`*
